Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
oops 5 pages

Since SNOWMED-CT nor ICD cover concepts pertaining to routine measured activity, we are devising a supplemental ontology for these concepts we call \emph{Activity-SENSE}.  This ontology encompasses patient activities, standard units of measure with which these activities are measured, and the ability to describe how and what kinds of sensors were used to sense the activity measured.  The intention is for Activity-SENSE records to, like those of SNOMED-CT, eventually be translatable to different languages and mapped to other similiar ontologies of behaviour.

The data collected by patients' devices has the potential to create a large volume of highly structured data. Some sensors
are collecting minute-by-minute data values form multiple sensors 24 hours a day, whereas 
EHRs tend to contain individual records for each clinical session. Therefore, existing methods of storing EHRs may
prove to be unsuitable for the large volumes of data from activity diaries. However, integrating with existing EHRs
would enable clinicians and patients to view the data in context.

>>>>

Since SNOWMED-CT nor ICD cover routine measured activity, we are devising a supplemental ontology for these concepts called \emph{Activity-SENSE}.  This ontology encompasses patient activities, and standard units of measure with which activities are measured, as well as the ability to describe the sensors used.  The intention is for Activity-SENSE records to, like those of SNOMED-CT, eventually be translatable to different languages and mapped to other similiar ontologies of behaviour.

The data collected by patients' devices has the potential to create a large volumes of highly structured data. Some sensors
are collecting minute-by-minute data values form multiple sensors 24 hours a day, whereas 
EHRs tend to contain individual records for each clinical session. Therefore, existing methods of storing EHRs may
prove to be unsuitable for the large volumes of data from activity diaries. However, integrating with existing EHRs
would enable clinicians and patients to view the data in context.
